Verifying Hierarchical Cache Coherence Protocols: a theorem-prover based modular, reusable proof

### 2014-02-03 paper/Intuition.tex
stuff

Any earlier clean cache has the latestValue, and data is
obtained from a clean cache

>>>>

Invariant \ref{conservative} can be proved by
further breaking them into the following invariants between a parent-child pair
of caches.

\begin{inv}
\textit{stateChange}:
\begin{enumerate}
\item A child sends a response to its parent iff it downgrades its state.
\item A parent sends a response to a child iff it upgrades the directory of
that child.
\item The state and the directory can change only on sending and receiving a
response.
\end{enumerate}
\label{stateChange}
\end{inv}

Invariant \textit{stateChange} can be proved directly from the atomic
transitions for MSI. Other protocols have similar atomic transitions obeying
these invariants.

\begin{inv}
\textit{inTransitChange}:
\begin{enumerate}
\item When a response is sent from a child $c$ at time $t$ for an address $a$,
and has not been received by the parent $p$ before time $t'$, $\forall t_i, t <
t_i \le t' @-> c.\state[a]$ at $t_i \le c.\state[a]$ at $t+1$ and $\forall t_i,
t \le t_i \le t' @->$ $p.\dstate[c][a]$ at $t_i \ge c.\state[a]$ at $t$.
\item When a response is sent from parent $p$ at time $t$ for an address $a$,
and has not been received by its child $c$ before time $t'$, $\forall t_i, t <
t_i \le t' @-> p.\dstate[c][a]$ at $t_i \ge p.\dstate[c][a]$ at $t+1$ and
$\forall t_i, t \le t_i \le t' @->$ $c.\state[a]$ at $t_i \le p.\dstate[c][a]$ at
$t$.
\end{enumerate}
\label{inTransitChange}
\end{inv}

\begin{inv}
\textit{noTransitEqual}: When no response is in transit for an address, then
the state of a cache for that address is the same as its parent's directory for
that cache and address.
\label{noTransitEqual}
\end{inv}

Using Invariants \ref{stateChange} to \ref{noTransit}, it is easy to prove
Invariant \ref{conservative}. If no response is in flight for an address, then
the parent's directory state of the cache for the address matches that of the
cache's state for that address. If there is a response from parent to child in
flight, then the corresponding directory at the parent will be no less than the
directory immediately after the response was sent and the state of the child
will be no greater than the directory immediately before the response was sent
(by Invariant \textit{inTransitChange}). By Invariant \textit{stateChange}, the
parent upgrades the directory when sending the response, thus conforming to
Invariant \textit{conservative}. Similarly, it can be shown that if there is a
response from child to parent, Invariant \textit{coservative} will hold.

\begin{inv}
\textit{prevState}: When a response is received from a child to the parent
(parent to child) for an address, the state of the child for that address at
the time of sending (receiving) the response is the same as the parent's
directory for that child and address at the time of receiving (sending) the
response.
\label{prevState}
\end{inv}
